Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2021-06-19 ms/Thesis/thesis.tex
Add new time series graph

>>>>

%%% Figure: Time serires
%DC: TODO: fix this figure

\begin{figure}[h]
  \centering       
    \includegraphics[scale=0.5]{../Figures/Unstable_Time_series.eps}
    \includegraphics[scale=0.5]{../Figures/Stable_Time_series.eps}
    \caption{\textbf{Stable and unstable equilibrium dynamics} 
    The figure shows the frequency of cooperation over time (generations) starting from different initial frequencies.
    In \textbf{(a)} the system has unstable equilibrium and therefore, all the curves are moving away from it.
    In \textbf{(b)} the system has stable equilibrium and therefore, all the curves moves towards it. 
    Here, $T_A = 0.5$, $c = 0.5$,  $v=0.59$ and \textbf{(a)} $T_B = 0.4$, $\alpha=0.1$ and $b=1.2$. \textbf{(b) $T_B=0.7$, $\alpha=0.6$ and $b=2.3$}.}
    \label{fig:time_series}
\end{figure}
